Coupling PDEs on XD-YD domains with Lagrange multipliers

### 2019-05-07 stab/stab.tex
multiscale results

% SIAM Article Template
\documentclass[r]{siamart171218}
% Packages and macros go here
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{float}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumitem}  
\usepackage{epstopdf}
\usepackage{tikz}

@@

% REQUIRED
\begin{abstract}
  This note summarizes numerical experiments investigating stabilization
  techniques for coupled multiscale problems using Lagrange multipliers. 
\end{abstract}

@@

\section{Babu{\v s}ka problem}\label{sec:babuska}
Given bounded $\Omega\subset\mathbb{R}^2$, let $\Gamma_D$, $\Gamma_L \subset \partial \Omega$ be such that $\semi{\Gamma_i}\neq 0$,
$i\in\left\{D, L\right\}$, $\bigcup_{i}\Gamma_i=\partial\Omega$.
We then consider the Poisson problem 
\[
\begin{aligned}
-\Delta u &= f &\mbox{ in }\Omega,\\
u &= g &\mbox{ on }\Gamma_D,\\
u &= g &\mbox{ on }\Gamma_L,\\
\end{aligned}
\]
which upon introducing the Lagrange multiplier $p\in Q=(H^{1/2}_{00}(\Gamma_L))^{\prime}$
leads to a variational problem: Find $u\in V=H^1_{0, \Gamma_D}(\Omega)$,
$p\in Q$ such that
%
\begin{equation}\label{eq:bab}
  \begin{aligned}
    &\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v - \int_{\Gamma_N}h v &\forall v\in V,\\
    &\int_{\Gamma_L}q u  &\phantom{+\int_{\Omega} \nabla u\cdot \nabla v} &= \int_{\Gamma} g q &\forall q\in Q.
  \end{aligned}
\end{equation}
%

% FIXME: [OK]results in -0.5 norm
%        is 0.5 for P1 due to bcs?
%        image of the domain for Babuska
%        Babuska text
%        2d-1d-1d tables
%        2d-1d-1d domain image
%        2d-1d-1d text
%
%        H(div) case code
%        rest of it

@@

\subsubsection{Non-matching case} Here $\dim Q_H$ is (considerably) larger
than the trace space of $V_h$ and stabilization of \cite{burman2014projection}
is needed to obtain inf-sup stability. More precisely, the discretization
of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
\[
\begin{aligned}
&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v - \int_{\Gamma_N}h v &\forall v\in V_h,\\
  &\int_{\Gamma_L}q u  &-\gamma \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p\cdot\nabla q &= \int_{\Gamma} g q &\forall q\in Q_H.
  \end{aligned}
\]
Here $\gamma$ is a stabilization parameter and we use $\gamma=1$ in the
following. As before, Dirichlet boundary conditions $p=0$ on $\partial\Gamma_L$ are
enforced.

MinRes iteration counts with the Riesz map preconditioner are shown in
Table \ref{tab:p1_p1}. Here, the $Q$ block of the preconditioner is
defined as
\[
\langle (-\Delta_{00})^{1/2} \bullet, q\rangle + \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla \bullet \cdot\nabla q,\quad q\in Q_H.
\]
%

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{utters} & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$ \\
    \hline
8.84E-02 & 6.91E+00(--)   & 6.37E+00(--)   & 29 & 5.131 & 6.90E+00(--)  & 5.94E+00(--)    & 31 & 4.836\\
4.42E-02 & 3.54E+00(0.97) & 1.61E+00(1.98) & 26 & 5.176 & 3.54E+00(0.96) & 1.76E+00(1.75) & 29 & 4.846\\
2.21E-02 & 1.78E+00(0.99) & 5.45E-01(1.56) & 26 & 5.191 & 1.78E+00(0.99) & 5.95E-01(1.57) & 28 & 4.851\\
1.10E-02 & 8.93E-01(1.00) & 3.11E-01(0.81) & 25 & 5.195 & 8.93E-01(1.00) & 3.24E-01(0.88) & 26 & 4.853\\
5.52E-03 & 4.46E-01(1.00) & 2.12E-01(0.55) & 24 & 5.196 & 4.46E-01(1.00) & 2.16E-01(0.59) & 26 & 4.853\\
2.76E-03 & 2.23E-01(1.00) & 1.49E-01(0.51) & 24 & 5.196 & 2.23E-01(1.00) & 1.50E-01(0.52) & 24 & 4.854\\
1.38E-03 & 1.12E-01(1.00) & 1.06E-01(0.50) & 22 & --    & 1.12E-01(1.00) & 1.06E-01(0.51) & 22 & --   \\
    \hline
  \end{tabular}
  }
    \caption{Approximation errors, number of preconditioner MinRes iterations (\#) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P1 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p1}
  \end{center}
\end{table}
%
Concerning approximation properties of the discretization, note that the error
for the multiplier is reported in the $L^2$ norm and not the natural $H^{-1/2}$
norm. Nevertheless, the rate seems sub-optimal. This is likely due to the fact
that the multiplier in the manufactured test case does not satisfy the
Dirichlet boundary conditions employed in the discrete problem.

\subsection{Discretization by P1-P0 elements}\label{sec:p1_p0}
We consider finite element discretization of \eqref{eq:bab} in terms P1 elements
for the space $V$ while the multiplier space used piecewise constants elements
(P0). In both the matching and non-matching case the discretization is unstable
and inf-sup stability is obtained by using stabilization \cite{burman2014projection}.
That is, the disretization of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
\[
\begin{aligned}
&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v - \int_{\Gamma_N}h v &\forall v\in V_h,\\
  &\int_{\Gamma_L}q u  &-\gamma \sum_{\mathcal{V}^0} \avg{H_K}^2\jump{p}\jump{q} &= \int_{\Gamma} g q &\forall q\in Q_H,
  \end{aligned}
\]
where $\mathcal{V}^0$ is the set of all interior vertices of $\Gamma_H$.

@@

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$ \\
    \hline
8.84E-02 & 6.88E+00(--)   & 2.83E+00(--)  & 26 & 4.749  & 6.91E+00(--)   & 1.17E+01(--)  & 35 & 6.940 \\
4.42E-02 & 3.54E+00(0.96) & 2.12E+00(0.42)& 28 & 4.817  & 3.54E+00(0.96) & 2.33E+00(2.33)& 35 & 6.973 \\
2.21E-02 & 1.78E+00(0.99) & 7.42E-01(1.51)& 28 & 4.840  & 1.78E+00(0.99) & 4.91E-01(2.24)& 30 & 6.987 \\
1.10E-02 & 8.93E-01(1.00) & 2.17E-01(1.78)& 25 & 4.850  & 8.93E-01(1.00) & 1.46E-01(1.75)& 28 & 6.994 \\
5.52E-03 & 4.46E-01(1.00) & 8.90E-02(1.28)& 23 & 4.853  & 4.46E-01(1.00) & 5.90E-02(1.31)& 27 & 6.996 \\
2.76E-03 & 2.23E-01(1.00) & 4.28E-02(1.06)& 23 & 4.853  & 2.23E-01(1.00) & 2.77E-02(1.09)& 26 & 6.995 \\
1.38E-03 & 1.12E-01(1.00) & 2.12E-02(1.01)& 23 & --     & 1.12E-01(1.00) & 1.36E-02(1.02)& 25 & --    \\  
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioner MinRes iterations (\#) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P0 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p0}
  \end{center}
\end{table}

\section{Coupled multiscale problem}\label{sec:coupled} As a stepping stone
towards the coupled 3$d$-1$d$-1$d$ problem we consider first a coupled multiscale
problem where the dimensionality gap is 1. Given two bounded domains $\Omega^i \subset\mathbb{R}^2$,
$i=\left\{-, +\right\}$, let $\Gamma$ be the intersection of the domain boundaries,
cf. Figure \ref{fig:coupled_domain}. We are then interested in solving

\begin{minipage}{0.47\textwidth}
  \begin{equation}
    \begin{aligned}
      -\Delta u^i &= f &\mbox{ in }\Omega^{i}, i\in\left\{+, -\right\},\\
      u^i &= g^i &\mbox{ on }\partial\Omega^{i}\setminus\Gamma,\\
      \jump{u} &= 0 &\mbox{ on }\Gamma,\\
      -\Delta \hat{u} + \jump{\nabla u\cdot n}&= \hat{f} &\mbox{ on }\Gamma,\\
      \hat{u} &= \hat{g} &\mbox{ on }\partial\Gamma,\\
      u - \hat{u} &= g&\mbox{ on }\Gamma.\\
    \end{aligned}
\end{equation}
\null
\par\xdef\tpd{\the\prevdepth}
\end{minipage}
\hfill
\begin{minipage}{0.47\textwidth}
  \begin{figure}[H]
    \begin{center}
\begin{tikzpicture}
  \draw[black, very thick] (0,0) rectangle (4, 4);
  \draw[black, very thick] (2, 0) rectangle (2, 4);

  \node[fill=white, opacity=0.9] at (1, 2) {$\Omega^{-}$};
  \node[fill=white, opacity=0.9] at (3, 2) {$\Omega^{+}$};

  \draw[->, black] (2, 1) -- (3, 1);
  \node[fill=white, opacity=0.9, above] at (2.5, 1) {$n$};
  \node[fill=white, opacity=0.9, right] at (2.025, 2) {$\Gamma$};
\end{tikzpicture}
    \end{center}
    %\vspace{-20pt}
    \caption{Schematic domain coupled multiscale problem.}
    \label{fig:coupled_domain}
    %\vspace{5pt}    
\end{figure}
\end{minipage}
%

>>>>

% SIAM Article Template
\documentclass[r]{siamart171218}
% Packages and macros go here
\usepackage[english]{babel}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{float}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumitem}  
\usepackage{epstopdf}
\usepackage{tikz}

@@

% REQUIRED
\begin{abstract}
  This note summarizes numerical experiments investigating stabilization
  techniques for coupled multiscale problems using Lagrange multipliers.
  These are personal notes written to keep track of the developments on this
  topic, to be kept confidential.
\end{abstract}

@@

\section{Babu{\v s}ka problem}\label{sec:babuska}
Given bounded $\Omega\subset\mathbb{R}^2$, let $\Gamma_D$, $\Gamma_L \subset \partial \Omega$ be such that $\semi{\Gamma_i}\neq 0$,
$i\in\left\{D, L\right\}$, $\bigcup_{i}\Gamma_i=\partial\Omega$.
We then consider the Poisson problem 
\[
\begin{aligned}
-\Delta u &= f &\mbox{ in }\Omega,\\
u &= g &\mbox{ on }\Gamma_D,\\
u &= g &\mbox{ on }\Gamma_L,\\
\end{aligned}
\]
which upon introducing the Lagrange multiplier $p\in Q=(H^{1/2}_{00}(\Gamma_L))^{\prime}$
leads to a variational problem: Find $u\in V=H^1_{0, \Gamma_D}(\Omega)$,
$p\in Q$ such that
%
\begin{equation}\label{eq:bab}
  \begin{aligned}
    &\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V,\\
    &\int_{\Gamma_L}q u  &\phantom{+\int_{\Omega} \nabla u\cdot \nabla v} &= \int_{\Gamma} g q &\forall q\in Q.
  \end{aligned}
\end{equation}
%

@@

\subsubsection{Non-matching case} Here $\dim Q_H$ is (considerably) larger
than the trace space of $V_h$ and stabilization of \cite{burman2009interior}
is needed to obtain inf-sup stability. More precisely, the discretization
of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
%
\begin{equation}\label{eq:p1_stab}
\begin{aligned}
&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_h,\\
  &\int_{\Gamma_L}q u  &-\gamma \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p\cdot\nabla q &= \int_{\Gamma} g q &\forall q\in Q_H.
  \end{aligned}
\end{equation}
%
Here $\gamma$ is a stabilization parameter and we use $\gamma=1$ in the
following. As before, the trial and test functions of the space $Q_H$ are
constructed such that they satisfy the boundary conditions $p=0$ on $\partial\Gamma_L$.

MinRes iteration counts with the Riesz map preconditioner are shown in
Table \ref{tab:p1_p1}. Here, the $Q$ block of the preconditioner is based
on the inverse of the bilinear 
\[
\langle (-\Delta_{00})^{1/2} p, q\rangle + \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p \cdot\nabla q,\quad p, q\in Q_H.
\]
%

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.84E-02 & 6.91E+00(--)   & 6.37E+00(--)   & 29 & 5.131 & 6.90E+00(--)  & 5.94E+00(--)    & 31 & 4.836\\
4.42E-02 & 3.54E+00(0.97) & 1.61E+00(1.98) & 26 & 5.176 & 3.54E+00(0.96) & 1.76E+00(1.75) & 29 & 4.846\\
2.21E-02 & 1.78E+00(0.99) & 5.45E-01(1.56) & 26 & 5.191 & 1.78E+00(0.99) & 5.95E-01(1.57) & 28 & 4.851\\
1.10E-02 & 8.93E-01(1.00) & 3.11E-01(0.81) & 25 & 5.195 & 8.93E-01(1.00) & 3.24E-01(0.88) & 26 & 4.853\\
5.52E-03 & 4.46E-01(1.00) & 2.12E-01(0.55) & 24 & 5.196 & 4.46E-01(1.00) & 2.16E-01(0.59) & 26 & 4.853\\
2.76E-03 & 2.23E-01(1.00) & 1.49E-01(0.51) & 24 & 5.196 & 2.23E-01(1.00) & 1.50E-01(0.52) & 24 & 4.854\\
1.38E-03 & 1.12E-01(1.00) & 1.06E-01(0.50) & 22 & --    & 1.12E-01(1.00) & 1.06E-01(0.51) & 22 & --   \\
    \hline
  \end{tabular}
  }
    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P1 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p1}
  \end{center}
\end{table}
%
Concerning approximation properties of the discretization, note that the error
for the multiplier is reported in the $L^2$ norm and not the natural $H^{-1/2}$
norm. Nevertheless, the rate seems sub-optimal. This is likely due to the fact
that the multiplier in the manufactured test case does not satisfy the
Dirichlet boundary conditions employed in the discrete problem.

\subsection{Discretization by P1-P0 elements}\label{sec:p1_p0}
We consider finite element discretization of \eqref{eq:bab} in terms P1 elements
for the space $V$ while the multiplier space used piecewise constants elements
(P0). In both the matching and non-matching case the discretization is unstable
and inf-sup stability is obtained by using stabilization \cite{burman2014projection}.
That is, the disretization of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
%
\begin{equation}\label{eq:p0_stab}
\begin{aligned}
&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_h,\\
  &\int_{\Gamma_L}q u  &-\gamma \sum_{\mathcal{V}^0} \avg{H_K}^2\jump{p}\jump{q} &= \int_{\Gamma} g q &\forall q\in Q_H,
  \end{aligned}
\end{equation}
%
where $\mathcal{V}^0$ is the set of all interior vertices of $\Gamma_H$.

@@

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.84E-02 & 6.88E+00(--)   & 2.83E+00(--)  & 26 & 4.749  & 6.91E+00(--)   & 1.17E+01(--)  & 35 & 6.940 \\
4.42E-02 & 3.54E+00(0.96) & 2.12E+00(0.42)& 28 & 4.817  & 3.54E+00(0.96) & 2.33E+00(2.33)& 35 & 6.973 \\
2.21E-02 & 1.78E+00(0.99) & 7.42E-01(1.51)& 28 & 4.840  & 1.78E+00(0.99) & 4.91E-01(2.24)& 30 & 6.987 \\
1.10E-02 & 8.93E-01(1.00) & 2.17E-01(1.78)& 25 & 4.850  & 8.93E-01(1.00) & 1.46E-01(1.75)& 28 & 6.994 \\
5.52E-03 & 4.46E-01(1.00) & 8.90E-02(1.28)& 23 & 4.853  & 4.46E-01(1.00) & 5.90E-02(1.31)& 27 & 6.996 \\
2.76E-03 & 2.23E-01(1.00) & 4.28E-02(1.06)& 23 & 4.853  & 2.23E-01(1.00) & 2.77E-02(1.09)& 26 & 6.995 \\
1.38E-03 & 1.12E-01(1.00) & 2.12E-02(1.01)& 23 & --     & 1.12E-01(1.00) & 1.36E-02(1.02)& 25 & --    \\  
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P0 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p0}
  \end{center}
\end{table}

\section{Coupled multiscale problem}\label{sec:coupled} As a stepping stone
towards the coupled 3$d$-1$d$-1$d$ problem we consider first a coupled multiscale
problem where the dimensionality gap is 1. Given two bounded domains $\Omega^i \subset\mathbb{R}^2$,
$i\in\left\{-, +\right\}$, let $\Gamma$ be the intersection of the domain boundaries,
cf. Figure \ref{fig:coupled_domain}. We are then interested in solving

\begin{minipage}{0.47\textwidth}
  \begin{equation}\label{eq:coupled}
    \begin{aligned}
      -\Delta u^i &= f &\mbox{ in }\Omega^{i}, i\in\left\{+, -\right\},\\
      u^i &= g^i &\mbox{ on }\Gamma^i_D\partial\Omega^{i}\setminus\Gamma,\\
      \jump{u} &= 0 &\mbox{ on }\Gamma,\\
      -\Delta \hat{u} - \jump{\nabla u\cdot n}&= \hat{f} &\mbox{ on }\Gamma,\\
      \hat{u} &= \hat{g} &\mbox{ on }\partial\Gamma,\\
      u - \hat{u} &= h&\mbox{ on }\Gamma.\\
    \end{aligned}
\end{equation}
\null
\par\xdef\tpd{\the\prevdepth}
\end{minipage}
\hfill
\begin{minipage}{0.47\textwidth}
  \begin{figure}[H]
    \begin{center}
\begin{tikzpicture}
  \draw[black!60!white, very thick] (0,0) rectangle (4, 4);
  \draw[black!60!white, very thick] (2, 0) rectangle (2, 4);

  \node[black!60!white, fill=white, opacity=0.9] at (1, 2) {$\Omega^{-}$};
  \node[black!60!white, fill=white, opacity=0.9] at (3, 2) {$\Omega^{+}$};
  \node[black!60!white, fill=white, opacity=0.9, right] at (4, 0) {$\Gamma_D$};

  \draw[black, very thick] (2, 0) -- (2, 4);
  \draw[->, black] (2, 1) -- (3, 1);
  \node[fill=white, opacity=0.9, above] at (2.5, 1) {$n$};
  \node[fill=white, opacity=0.9, right] at (2.025, 2) {$\Gamma$};
\end{tikzpicture}
    \end{center}
    %\vspace{-20pt}
    \caption{Schematic domain of coupled multiscale problem.}
    \label{fig:coupled_domain}
    %\vspace{5pt}    
\end{figure}
\end{minipage}
%
Let $\Omega=\Omega^{+}\cup\Omega^{-}$ and $\Gamma_D=\Gamma^{+}_D\cup\Gamma^{-}_N$.
Introducing a Lagrange multiplier $p=\jump{\nabla\cdot n}\in Q=(H^{-1/2}_{00}(\Gamma))^{\prime}$
the weak form of \eqref{eq:coupled} reads: Find $u\in V=H^1_{0, \Gamma_D}(\Omega)$,
$\hat{v}\in\hat{V}=H^1_{0, \partial\Gamma}(\Gamma)$, $p\in Q$ such that
%
\begin{equation}\label{eq:coupled_weak}
  \begin{aligned}
    &\int_{\Omega}\nabla u\cdot \nabla v &\phantom{+\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &+\int{\Gamma}p v &= \int_{\Omega}f v \quad &\forall v\in V,\\
    &\phantom{\int_{\Omega}\nabla u\cdot \nabla v} &+{\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &-\int{\Gamma}p\hat{v} &= \int_{\Gamma}\hat{f}\hat{v} \quad &\forall \hat{v}\in \hat{V},\\
    &\int_{\Gamma}u q &-\int_{\Gamma}\hat{u}q &\phantom{-\int{\Gamma}q\hat{v}} &= \int_{\Gamma}h q \quad &\forall q\in Q.
  \end{aligned}
\end{equation}
%
\begin{figure}[h]
  \begin{center}
    \begin{tikzpicture}[scale=0.60]
      % Minus
  \draw[black, very thick] (1,0) rectangle (4, 3);
  \draw[black, very thick] (1,0) -- (4, 3);
  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega^{-}_{h}$};

  \draw[black, thin, dotted] (4, 0) -- (4.5, 0);
  \draw[black, thin, dotted] (4, 3) -- (4.5, 3);
  % Center
  \draw[black, thin, dotted] (4.5, 0) -- (5, 0);
  \draw[black, thin, dotted] (4.5, 3) -- (5, 3);

  \draw[black, very thick] (4.5,0) -- (4.5, 3);
  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{H}$};

  \node[mark size=3pt, color=black] at (4.5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 3) {\pgfuseplotmark{*}};
  % Right
    \draw[black, very thick] (5,0) rectangle (8, 3);
  \draw[black, very thick] (5,0) -- (8, 3);
  \node[fill=white, opacity=0.9] at (6.5, 1.5) {$\Omega^{+}_{h}$};

  \node[mark size=3pt, color=black] at (5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (5, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
    %
    \hspace{10pt}
    \begin{tikzpicture}[scale=0.60]
      % Minus
  \draw[black, very thick] (1,0) rectangle (4, 3);
  \draw[black, very thick] (1,0) -- (4, 3);
  \node[fill=white, opacity=0.9] at (2.75, 1.5) {$\Omega^{-}_{h}$};

  \draw[black, thin, dotted] (4, 0) -- (4.5, 0);
  \draw[black, thin, dotted] (4, 3) -- (4.5, 3);
  % Center
  \draw[black, thin, dotted] (4.5, 0) -- (5, 0);
  \draw[black, thin, dotted] (4.5, 3) -- (5, 3);
     % Center
  \draw[black, very thick] (4.5,0) -- (4.5, 3);
  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{H}$};

  \node[mark size=3pt, color=black] at (4.5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 1) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 2) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 3) {\pgfuseplotmark{*}};
  % Right
    \draw[black, very thick] (5,0) rectangle (8, 3);
  \draw[black, very thick] (5,0) -- (8, 3);
  \node[fill=white, opacity=0.9] at (6.5, 1.5) {$\Omega^{+}_{h}$};

  \node[mark size=3pt, color=black] at (5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (5, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (8, 3) {\pgfuseplotmark{*}};
    \end{tikzpicture}
        %
    \hspace{10pt}
    \begin{tikzpicture}[scale=0.60]
      % Minus
  \draw[black, very thick] (0,0) rectangle (3, 3);
  \draw[black, very thick] (0,0) -- (3, 3);
  \node[fill=white, opacity=0.9] at (2.25, 1.5) {$\Omega^{-}_{h}$};

  \node[mark size=3pt, color=black] at (0.0, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (3.0, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (0.0, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (3.0, 3) {\pgfuseplotmark{*}};

     % Center
  \draw[black, very thick] (4.5,0) -- (4.5, 3);
  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{H}$};

  \node[mark size=3pt, color=black] at (4.5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 1) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 2) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (4.5, 3) {\pgfuseplotmark{*}};

  \draw[black, very thick] (3,0) -- (6, 0);
  \draw[black, very thick] (3,0) -- (6, 3);
  \draw[black, very thick] (3,3) -- (6, 3);  
  % Right
    \draw[black, very thick] (6,0) rectangle (9, 3);
  \draw[black, very thick] (6,0) -- (9, 3);
  \node[fill=white, opacity=0.9] at (6.75, 1.5) {$\Omega^{+}_{h}$};

  \node[mark size=3pt, color=black] at (6, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (6, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
%
\end{center}
  \caption{Different mesh settings considered for the coupled problem
    \eqref{eq:coupled_weak}: conforming matching, conforming non-matching,
    non-conforming (from left to right).
  }
\label{fig:multi_domains}
\end{figure}
%
In the following $\Omega=(0, 1)$, $\Gamma=\left\{(x, y)\in\Omega; x=\tfrac{1}{2}\right\}$
and based on the properties of the finite element meshes $\Omega_h$, $\Gamma_H$
we shall distinguish three different settings, cf. Figure \ref{fig:multi_domains}.
Here, a conforming case implies that the trace mesh of $\Omega_h$ on $\Gamma$
consists only of the existing facets of the mesh. In the conforming setting 
we consider matching and non-matching cases as defined above. Let us also
remark that the approximation of the space $\hat{V}$ shall always be constructed
on the multiplier mesh $\Gamma_H$.

\subsubscection{P1-P1-P1 discretization with $\Gamma$ conformity}

\begin{table}
  \begin{center}
    \scriptsize{
  \begin{tabular}{c|ccc|c|c||ccc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.8E-2 & 8.8E-1(--)   & 2.0E0(--)    & 8.9E-1(--)   & 20 & 8.0 & 8.6E-1(--)   & 6.7E-1(--)   & 1.7E-1(--)   & 23 & 4.5  \\
4.4E-2 & 4.4E-1(1.01) & 1.0E0(0.99)  & 2.1E-1(2.10) & 22 & 8.4 & 4.4E-1(0.99) & 3.4E-1(1.00) & 4.5E-2(1.89) & 25 & 4.5  \\
2.2E-2 & 2.2E-1(1.00) & 5.0E-1(1.00) & 5.1E-2(2.03) & 22 & 8.5 & 2.2E-1(1.00) & 1.7E-1(1.00) & 1.2E-2(1.95) & 25 & 4.6  \\
1.1E-2 & 1.1E-1(1.00) & 2.5E-1(1.00) & 1.3E-2(2.01) & 21 & 8.6 & 1.1E-1(1.00) & 8.4E-2(1.00) & 3.0E-3(1.98) & 24 & 4.7  \\
5.5E-3 & 5.5E-2(1.00) & 1.3E-1(1.00) & 3.2E-3(2.00) & 21 & 8.7 & 5.5E-2(1.00) & 4.2E-2(1.00) & 7.5E-4(1.99) & 24 & 4.7  \\
2.8E-3 & 2.7E-2(1.00) & 6.3E-2(1.00) & 7.9E-4(2.00) & 21 & 8.7 & 2.7E-2(1.00) & 2.1E-2(1.00) & 1.9E-4(1.99) & 22 & 4.7  \\
1.4E-3 & 1.4E-2(1.00) & 3.1E-2(1.00) & 2.0E-4(2.00) & 21 & --  & 1.4E-2(1.00) & 1.0E-2(1.00) & 4.7E-5(2.00) & 22 & --   \\
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
      with P1-P1-P1 elements. Conforming (left) matching and (right) non-matching case.}
  \label{tab:coupled_p1_p1}
  \end{center}
\end{table}

% --------------------------------------------------------------------

\subsubscection{P1-P1-P0 discretization with $\Gamma$ conformity}

\begin{table}
  \begin{center}
    \scriptsize{
  \begin{tabular}{c|ccc|c|c||ccc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.8E-2 & 9.3E-1(--)   & 2.0E0(--)    & 2.9E0(--)    & 21 & 4.5 & 8.6E-1(--)   & 6.7E-1(--)   & 9.2E-1(--)   & 29 & 7.8\\
4.4E-2 & 4.4E-1(1.06) & 1.0E0(0.99)  & 1.1E0(1.43)  & 28 & 4.8 & 4.4E-1(0.99) & 3.4E-1(1.00) & 3.4E-1(1.42) & 31 & 8.1\\
2.2E-2 & 2.2E-1(1.02) & 5.0E-1(1.00) & 4.1E-1(1.39) & 28 & 5.0 & 2.2E-1(1.00) & 1.7E-1(1.00) & 1.4E-1(1.34) & 32 & 8.3\\
1.1E-2 & 1.1E-1(1.00) & 2.5E-1(1.00) & 1.7E-1(1.28) & 27 & 5.1 & 1.1E-1(1.00) & 8.4E-2(1.00) & 5.6E-2(1.26) & 30 & 8.4\\
5.5E-3 & 5.5E-2(1.00) & 1.3E-1(1.00) & 7.5E-2(1.19) & 27 & 5.2 & 5.5E-2(1.00) & 4.2E-2(1.00) & 2.5E-2(1.18) & 30 & 8.5\\
2.8E-3 & 2.7E-2(1.00) & 6.3E-2(1.00) & 3.5E-2(1.11) & 27 & 5.2 & 2.7E-2(1.00) & 2.1E-2(1.00) & 1.1E-2(1.11) & 29 & 8.5\\
1.4E-3 & 1.4E-2(1.00) & 3.1E-2(1.00) & 1.7E-2(1.07) & 27 & --  & 1.4E-2(1.00) & 1.0E-2(1.00) & 5.5E-3(1.06) & 29 & -- \\
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
      with P1-P1-P0 elements. Conforming (left) matching and (right) non-matching case.}
  \label{tab:coupled_p1_p0}
  \end{center}
\end{table}
